\documentclass[10pt]{article}

% NeurIPS 2026 workshop proposal -- cleaned source-faithful draft.
% This version preserves the proposal structure and substance from the
% uploaded source, adds explicit Part I / Part II headers, fixes minor
% presentation issues, and wires verified literature/workshop references
% into the prose.
%
% Page budget (NeurIPS 2026 hard limit):
%   - Pages 1-3: main proposal
%   - Pages 4-5: organizer information
%   - Reference materials / appendices (reviewer roster): unlimited.

% THIS IS THE PREAMBLE
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{xcolor}
\usepackage{float}
\definecolor{AIDaRBlue}{HTML}{0645AD}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}

\newcommand{\speakername}[1]{\textcolor{AIDaRBlue}{#1}}
\newcommand{\confirmed}{\textit{confirmed}}
\newcommand{\tentative}{\textit{tentative}}

\IfFileExists{neurips_2026.sty}{%
  \usepackage[final]{neurips_2026}%
}{%
  \usepackage[letterpaper,top=0.75in,bottom=0.85in,left=0.8in,right=0.8in]{geometry}%
  \usepackage{times}%
}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{array}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{fancyhdr}

% Tighten vertical rhythm so the main proposal fits in 3 pages.
\setlength{\parskip}{1.8pt}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=1.1em,itemsep=0pt,topsep=0pt,parsep=0pt}

% Compact research-paper-style headings. Sections and subsections both display.
\titleformat*{\section}{\normalsize\bfseries}
\titleformat*{\subsection}{\normalsize\bfseries}
\titleformat{\subsubsection}[runin]{\normalfont\bfseries\itshape}{}{0pt}{}[\,]
\titlespacing*{\section}{0pt}{5pt}{1pt}
\titlespacing*{\subsection}{0pt}{3pt}{0.5pt}
\titlespacing*{\subsubsection}{0pt}{2pt}{0.4em}
\titlespacing*{\paragraph}{0pt}{2pt}{0.4em}

% Numbering depth: number sections and subsections (and show them in the body).
\setcounter{secnumdepth}{3}

% Tighter title block.
\makeatletter
\renewcommand{\maketitle}{%
  \begin{center}%
    {\Large\bfseries \@title\par}%
    \vspace{2pt}%
    {\normalsize \@author\par}%
  \end{center}%
  % \vspace{-4pt}%
}
\makeatother

\hypersetup{
  colorlinks=true,
  linkcolor=black,
  citecolor=black,
  urlcolor=blue
}


% Visible proposal split and running headers.
\newcommand{\currentproposalpart}{Main Workshop Proposal}
\newcommand{\setproposalpart}[1]{\gdef\currentproposalpart{#1}}
\setlength{\headheight}{12pt}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\footnotesize\currentproposalpart}
\fancyhead[R]{\footnotesize AIDaR @ NeurIPS 2026\quad\thepage}
\renewcommand{\headrulewidth}{0.25pt}
\newcommand{\proposalbanner}[2]{%
  % \vspace{-4pt}%
  \noindent\colorbox{black!8}{\parbox{\dimexpr\linewidth-2\fboxsep\relax}{\textbf{#1}\hfill\textit{#2}}}%
  \vspace{2pt}%
}


\title{AIDaR: Data Infrastructure and Benchmarks for Scientific AI}

\author{NeurIPS 2026 Workshop Proposal}

\date{}

\begin{document}

\setproposalpart{PART I -- Main Workshop Proposal}
\proposalbanner{PART I -- Main Workshop Proposal}{Pages 1--3, three-page limit}
\maketitle

% \begin{center}
% \textit{\textbf{How do we know scientific data is ready for reliable, trustworthy AI?}}
% \end{center}

\vspace{2pt}
\textbf{Tagline (\textless 140 chars):} \textit{From experimental data to reliable scientific AI systems.}\\

% \vspace{-2pt}
\begin{abstract}
Scientific AI is moving from curated prediction tasks toward systems that work directly with experimental data. Foundation models, retrieval systems, and agents are being asked to use experimental data, query scientific knowledge, run analyses, and support follow-up decisions. Scientific data must remain connected to samples, assays, protocols, measurements, workflow outputs, and the context needed to interpret results outside the lab or notebook where the data was produced.

AIDaR focuses on two problems in this transition. First, how should scientific data be organized so models and agents can use it: from raw measurements and analysis-ready files to relational or graph-structured knowledge, multimodal biomedical measurements, workflow systems, and large industrial datasets used for model training and wet-lab feedback? Second, how should evaluations determine where frontier models are reliable: across biological reasoning, practical data analysis, retrieval over structured scientific knowledge, assay-specific workflows, and deployed scientific AI systems?

The workshop will bring together researchers, industry scientists, and engineers building scientific data systems, foundation models, agents, biomedical evaluations, and industrial assay platforms. The program includes invited talks, contributed papers, demos, panels, and breakout groups focused on AI-facing data infrastructure, practical evaluations, and concrete lessons from scientific AI deployments.
\end{abstract}

% =====================================================================
% 1. A Provisional AI Data Readiness Framework
% =====================================================================

\section{Workshop Tracks}

Scientific AI systems need data they can operate on and tests that show whether they used it correctly. AIDaR is organized around two tracks.

\paragraph{Track 1: AI-facing scientific data infrastructure.}
Scientific data must move from raw measurements into forms that models, retrieval systems, and agents can use. This includes linking files to samples and assay conditions, preserving the steps that produced an analysis-ready dataset, representing scientific relationships as tables, graphs, or knowledge networks, and exposing data through tools that scientists and agents can both use. Topics include data infrastructure for scientific foundation models, relational and graph-structured scientific data, multimodal biomedical measurements, assay-specific context, workflow systems, and large industrial datasets used for model training and wet-lab feedback.

\paragraph{Track 2: Benchmarks and evaluations for scientific AI.}
Scientific AI systems should be tested on tasks that resemble real scientific work. This includes choosing inputs, running analyses, checking controls, interpreting noisy results, and recovering biological or physical conclusions from data. Topics include biological reasoning and data-analysis tasks, retrieval and reasoning over structured scientific knowledge, evaluation of multimodal biomedical data, practical biology benchmarks, failure analysis, and studies of where model or agent performance changes across assays, platforms, workflows, or data organization choices.

Recent work on FAIR scientific data, dataset documentation, ML-ready metadata, AI-ready data, and scientific data-readiness pipelines motivates this workshop. AIDaR connects those efforts to scientific foundation models, retrieval systems, agents, and practical scientific AI evaluation~\cite{wilkinson2016fair,gebru2021datasheets,pushkarna2022datacards,akhtar2024croissant,brewer2025scientific,brewer2026pipeline,majithia2026actionable,hiniduma2024survey}.

% =====================================================================
% 2. Why Now
% =====================================================================
\section{Why Now}
\label{sec:why-now}

Scientific AI is moving from models trained on curated datasets to systems that interact with experimental data, scientific literature, databases, and lab workflows. These systems need data that preserves sample, assay, protocol, measurement, and workflow context.

Modern scientific data systems are not organized for this style of use. Raw instrument data, sample tables, images, count matrices, workflow outputs, notebooks, and plots are often split across storage systems, LIMS/ELN tools, workflow runners, and lab-specific conventions. Large industrial datasets add further pressure: perturbation datasets, multiplexed screens, tissue-model systems, and wet-lab feedback loops must be connected to model-training datasets and analysis tools.

Evaluations now shape where frontier models can be used in scientific work. A model that performs well on general reasoning may still fail on a specific assay, platform, analysis workflow, or data modality. Practical evaluations help identify where agents can assist scientists, where human review is required, and where results are not reliable enough to support follow-up experiments or operational decisions.

AIDaR is timely because these problems sit between model development and scientific use. The workshop brings together researchers, industry scientists, and engineers building scientific data systems, foundation models, agents, biomedical evaluations, industrial assay platforms, and deployed analysis environments.

\subsection{Target audience}
AIDaR is for researchers, scientists, and engineers building AI systems that must work with real scientific data. The audience includes AI-for-science researchers, foundation-model and agent builders, scientific RAG researchers, computational biologists, biomedical ML researchers, benchmark and evaluation researchers, data-management and provenance researchers, and teams responsible for assay data, workflow systems, LIMS/ELN integrations, model-training datasets, and deployed analysis tools.

We expect a medium-sized workshop: \textbf{100--200 attendees} and approximately \textbf{40--50 submissions}. We will welcome both methods papers and practitioner reports, including scientific data-system case studies, workflow and tool demos, evaluation suites, failure analyses, assay metadata schemas, retrieval benchmarks, agent task suites, and lessons from deployed scientific AI systems.

\subsection{Difference from related workshops} 
\label{sec:relationship}
AIDaR sits between AI-for-science workshops, dataset venues, and reliable-ML workshops. The NeurIPS AI for Science series addresses broad methods and bottlenecks for AI-enabled discovery; ML4PS focuses on machine learning for physical sciences; FM4LS focuses on multimodal foundation models and LLMs for life-science data; Data-Centric ML and the NeurIPS Datasets \& Benchmarks track focus on datasets, benchmarks, and data-centric ML methods; Reliable ML from Unreliable Data emphasizes missing, corrupted, shifted, adversarial, or strategic data; and ADSD 2025 at ICDM focuses on creating, curating, and benchmarking AI-ready scientific datasets \cite{ai4science2025,ml4ps2025,fm4ls2025,dmlr2025,reliableml2025,adsd2025}. 

AIDaR focuses on what happens after scientific data is produced: how it is organized for models and agents, how it appears inside real analysis workflows, and how to tell whether an AI system used it correctly. Compared with broad AI-for-science workshops, AIDaR is more focused on data infrastructure. Compared with dataset venues, it is more focused on use rather than publication. Compared with reliable-ML workshops, it is more focused on scientific workflows, assays, and deployed analysis environments.

The recent AI-ready-data literature and ADSD/ICPP activity show growing interest in the topic; AIDaR would be the first NeurIPS workshop centered on AI-facing scientific data systems and practical evaluations for scientific AI \cite{brewer2025scientific,brewer2026pipeline,majithia2026actionable}.

\subsection{Workshop History and Concurrent Submissions}
\label{sec:history}
This workshop has not previously been held at NeurIPS or another venue. No listed organizer is concurrently proposing another NeurIPS 2026 workshop.

% =====================================================================
% 3. Program, speakers, logistics, and compliance
% =====================================================================
\section{Program Format, Speakers, and Diversity}
\label{sec:program}

% \subsection{Program Format}
\subsection{Interactive one-day format}
\label{sec:format}
AIDaR is designed as a one-day in-person workshop within the 7--9 hour NeurIPS format. The program deliberately avoids a talks-only structure: invited talks are short, contributed work is central, posters/demos receive substantial time, and the afternoon breakout groups produce short written outputs for the post-workshop report. Any remote presentation will be used only for unforeseen emergencies and will remain within the NeurIPS one-hour cap.

% \vspace{-2pt}
\begin{table}[H]
\centering
\scriptsize
\caption{Draft one-day agenda. Confirmed speakers are listed in Section~\ref{sec:speakers}; remaining panel slots may be filled by additional confirmed panelists or accepted contributed work. All times are local and may shift by venue.}
\setlength{\tabcolsep}{3pt}
\renewcommand{\arraystretch}{1.12}
\begin{tabular}{@{}p{0.14\linewidth}p{0.43\linewidth}p{0.36\linewidth}@{}}
\toprule
\textbf{Time} & \textbf{Session} & \textbf{Topic / AIDaR lens} \tabularnewline
\midrule

08:45--09:10 &
Arrival, question wall, opening remarks, COI/LLM policies, and workshop tracks &
What experimental data must retain, and where evaluations show reliable AI use \tabularnewline

09:10--10:00 &
Invited talks: Max Welling (University of Amsterdam), and Jure Leskovec (Stanford) &
Scientific AI systems need AI-operable data: foundation models, materials discovery platforms, relational scientific data, and retrieval/reasoning over structured knowledge \tabularnewline

10:00--10:30 &
Coffee + poster/demo previews &
Early visibility into submitted benchmarks, tools, datasets, and case studies \tabularnewline

10:30--11:20 &
Contributed spotlights: Scientific data systems and practical evaluations &
Short talks on data schemas, experimental metadata, workflow interfaces, retrieval tasks, agent benchmarks, and failure cases from scientific AI systems \tabularnewline

11:20--12:00 &
Panel 1: Benchmarking AI on practical biology. Harihara Muralidharan (LatchBio), Kexin Huang (Phylo/Biomni), Pablo Meher Rojas (IBM/Dream Challenge) and Jon Laurent (Edison Scientific) &
How to construct biological and biomedical evaluations that approximate realistic scientific work, especially biological reasoning and practical data-analysis tasks.\tabularnewline

12:00--13:15 &
Poster/demo session 1 + lunch &
Community discussion around accepted papers, demos, tools, datasets, and emerging benchmark proposals \tabularnewline

13:15--14:00 &
Invited talks: Marianna Rapsomaniki (University of Lausanne), and Chloe-Agathe Azencott (Mines Paris–PSL) &
Biomedical data must preserve experimental meaning: assay design, sample and tissue context, treatment conditions, multimodal measurements, biological signal, and reproducibility \tabularnewline

14:00--14:50 &
Contributed spotlights: analysis histories and deployment lessons &
Short talks on workflow records, human review, failed analyses, and what scientific AI systems need to reproduce results \tabularnewline

14:50--15:40 &
Poster/demo session 2 + coffee &
Discussion of accepted tools, datasets, workflow systems, benchmark tasks, and lessons from deployed scientific AI systems \tabularnewline

15:40--16:25 &
Breakout groups: AI-facing data infrastructure for large industrial datasets: ManifoldBio, Polyphron, Tahoe Therapeutics, and LigandAI {\color{red} \textbf{TO CONFIRM}} &
Small-group work on large perturbation datasets, multiplexed in vivo screens, tissue-foundry systems, training large models, and integrating wet-lab feedback \tabularnewline

16:25--17:05 &
Panel 2: Engineering AI-operable assay data systems. Hoifung Poon (Microsoft Research) and additional industry panelists from TakaraBio, Vizgen, AtlasXOmics and Portal {\color{red} \textbf{TO DO}} &
Sample metadata, raw instrument data, analysis-ready files, workflow inputs and outputs, version history, and scientist-facing interfaces for deployed scientific AI systems \tabularnewline

17:05--17:45 &
Breakout report-out, community roadmap, closing remarks, and post-workshop report plan &
Next steps for AI-facing data systems, practical evaluations, and shared examples from scientific deployments \tabularnewline

\bottomrule
\end{tabular}
\end{table}



\subsection{Speakers and Panelists}
\label{sec:speakers}

Confirmed invited speakers and panelists include Max Welling (University of Amsterdam), Marianna Rapsomaniki (University of Lausanne), Jure Leskovec (Stanford), Chloe-Agathe Azencott (Mines Paris–PSL), Additional panelists are being finalized; any unfilled panel slots will be replaced by accepted contributed work or moderated discussion among confirmed participants.

The invited-speaker program develops the workshop's two tracks. Max Welling and Jure Leskovec open with AI-operable scientific data systems: heterogeneous data for foundation models and discovery platforms, and relational/graph infrastructure for retrieval and reasoning. Marianna Rapsomaniki and Chloe-Agathe Azencott then ground the evaluation track in biomedical data: assay design, sample and tissue context, treatment conditions, multimodal measurements, biological signal, and reproducibility.

\subsection{Panels}
\label{sec:panels}

The two panels focus on the workshop's two tracks. Panel 1, ``Benchmarking AI on practical biology,'' will focus on how to construct evaluations that approximate realistic scientific work, especially biological reasoning and data-analysis tasks that are useful in practice, rather than only ranking model accuracy on static benchmarks. Panelists include Harihara Muralidharan (LatchBio), Kexin Huang (Phylo/Biomni), Pablo Meher Rojas (IBM/Dream Challenge), and Jon Laurent (Edison Scientific).

Panel 2, ``Engineering AI-operable assay data systems,'' will focus on the infrastructure required to make experimental data usable by deployed scientific AI systems: sample metadata, raw instrument data, analysis-ready files, workflow inputs and outputs, version history, and scientist-facing interfaces. Panelists include Hoifung Poon (Microsoft Research), with additional industry panelists from TakaraBio, Vizgen, AtlasXOmics, and Portal under discussion. Confirmed panelists are expected to attend in person.

\subsection{Breakout groups}
\label{sec:breakouts}
Breakout groups will focus on AI-facing data infrastructure for large industrial datasets, with expected participation from ManifoldBio, Polyphron, Tahoe Therapeutics, and LigandAI. Participants will discuss how to organize data from large perturbation datasets, multiplexed in vivo screens, and tissue-foundry systems so models and agents can use it. Topics include molecule and protein designs, perturbations, doses, donor and tissue context, sequencing or imaging readouts, assay outcomes, model-training datasets, and links from model predictions back to wet-lab follow-up. Groups will identify where current data organization breaks down as datasets move from experimental platforms into model training, retrieval, and agent-guided analysis, then report concrete recommendations for the post-workshop report.


\subsection{Diversity, Inclusion, and Community Building}
\label{sec:diversity}

AIDaR is designed to bring together communities that rarely interact in the same venue: AI-for-science researchers, scientific data-infrastructure builders, benchmark and evaluation researchers, provenance and data-management experts, and practitioners deploying AI systems in high-stakes scientific settings. The organizing team and program committee span academia, industry research, biotechnology, scientific infrastructure, and data systems, with diversity across geography, seniority, discipline, institution type, and research perspective.

The workshop format is intentionally participatory rather than talks-only. Posters, demos, contributed spotlights, panels, and breakout groups are designed to give junior researchers, practitioners, tool builders, and domain scientists multiple opportunities to contribute. The CFP will explicitly welcome early-stage work, benchmarks, benchmark failures, lessons learned from unsuccessful AI data preparation efforts, tools, datasets, evaluation protocols, case studies, negative results, failed deployments, and postmortems of AI failures linked to data conditions.

We will also support community building beyond the workshop itself through lightweight mentoring for first-time authors, cross-domain collaboration, and breakout groups focused on readiness definitions, benchmark-design principles, and provenance-aware evaluation.

\section{Logistics, review process, and compliance}
\subsection{Submissions, review, COI, and LLM policy}
All submissions will be managed through OpenReview. We will accept non-archival short papers, extended abstracts, benchmarks/tools, demos, and position papers; the CFP will state the access policy and discourage work already accepted at the main NeurIPS conference or another archival ML venue. Invited speakers will be asked not to repeat main-conference or near-identical workshop talks.

Each submission will receive three reviews where possible. The PC will be sized so that no reviewer is assigned more than three papers; with 40--50 expected submissions, this requires 45--50 reviewers, with extra reviewers or area chairs if submissions exceed 70. Organizers will not give invited talks, submit papers, or shape decisions for conflicted submissions. Reviewers will be instructed not to use LLMs in reviewing, consistent with NeurIPS 2026 guidance.

\subsection{Timeline}
\label{sec:timeline}

\textbf{July 2026:} Website and CFP launch. \\
\textbf{August 2026:} Submission deadline. \\
\textbf{September 2026:} Review, meta-review, and notifications. \\
\textbf{October 2026:} Final materials and public schedule. \\
\textbf{December 2026:} Workshop.

\subsection{Location preference and technical needs:} Preferred order: \textbf{Paris, Atlanta, Sydney}; any venue is acceptable if needed. Technical needs are standard: projector/screen, podium microphone, Q\&A microphone, panel microphones/table, poster boards, and standard recording/livestream support. No special hardware is required.

\section{Expected Outcomes}
\label{sec:outcomes}
Concrete deliverables of the workshop will include: (i)~a public post-workshop report on open problems in AI-facing scientific data systems and practical evaluations; (ii)~examples of data-system patterns for samples, assays, workflow runs, model-training datasets, and wet-lab feedback; (iii)~recommendations for evaluating scientific AI systems in specific task contexts; (iv)~a collection of failure cases from scientific AI deployments and benchmarks; and (v)~a seed network of researchers, industry scientists, and engineers to develop future shared tasks and infrastructure examples.


% =====================================================================
% 6. Organizer Information -- two pages maximum (NeurIPS 2026 hard limit).
% =====================================================================
\newpage
\setproposalpart{PART II -- Organizer Information}
\proposalbanner{PART II -- Organizer Information}{Pages 4--5, two-page limit}
\section{Organizer Information}
\label{sec:organizers}

% \subsection{Note on This Section}
% \label{sec:org-note}
% Per NeurIPS 2026 guidance, this section is limited to two pages.

\subsection{COI and Concurrent-Proposal Statement}
\label{sec:org-coi}
Each listed organizer will confirm in writing, prior to OpenReview submission, that (a)~they are not listed on more than two NeurIPS 2026 workshop proposals, (b)~they understand that organizers cannot give invited talks at this workshop and will limit their on-stage role to brief introductions or panel moderation, and (c)~they will not submit papers to this workshop, nor will their students, postdocs, or close collaborators. Organizers will not review or shape acceptance decisions about submissions from within their own organization (corporation-wide for large corporations).

\subsection{Organizing Team}
\label{sec:org-team}

%\small

\noindent\textbf{Michal Rosen-Zvi.}
\textit{The Hebrew University of Jerusalem; IBM Research; 
\href{mailto:michal.rosen-zvi@mail.huji.ac.il}{michal.rosen-zvi@mail.huji.ac.il}.}
Director of AI for Healthcare and Life Sciences at IBM Research and Adjunct Professor of Computational Medicine at the Hebrew University. Her research focuses on machine learning for healthcare, scientific discovery, and biomedical AI. She leads multiple large-scale AI initiatives spanning pharmaceutical research, scientific reasoning, and AI-driven discovery systems.

\medskip

\noindent\textbf{Zoe Piran.}
\textit{Stanford University; Roche / Genentech;
\href{mailto:piran.zoe@gene.com}{piran.zoe@gene.com}.}
Postdoctoral Fellow at Genentech and Stanford University working at the intersection of machine learning and computational biology. Her research develops computational methods for understanding cellular dynamics from multimodal biological data and connects modern ML techniques with scientific discovery workflows.

\medskip

% \noindent\textbf{Shirley Ho.}
% \textit{New York University; Simons Foundation; 
% \href{mailto:shirley@polymathic.org}{shirley@polymathic.org}.}
% Astrophysicist and machine learning researcher whose work spans cosmology, foundation models for science, and interpretable machine learning. She has pioneered the application of modern deep learning methods in astrophysics and is a leading advocate for AI-driven scientific discovery.

\medskip

\noindent\textbf{Kenny Workman.}
\textit{LatchBio;
\href{mailto:kenny@latch.bio}{kenny@latch.bio}.}
Co-founder and CTO of LatchBio developing infrastructure and benchmarks for data analysis agents. His interests span engineering in biology, computing and AI.

\medskip

\noindent\textbf{Edaeni Hamid.}
\textit{Roche / Genentech;
\href{mailto:hamid.edaeni@gene.com}{hamid.edaeni@gene.com}.}
Machine learning and data-platform practitioner focused on deploying AI systems across complex scientific and enterprise data ecosystems. Her interests include AI data readiness, scientific data infrastructure, evaluation, and operationalizing AI systems in research environments.

\medskip

\noindent\textbf{Vladimir Ermakov.}
\textit{Edison Scientific;
\href{mailto:vermakov@edisonscientific.com}{vermakov@edisonscientific.com}.}
Researcher and entrepreneur building AI systems for scientific discovery, biomedical research, and foundation-model applications. His work focuses on scientific reasoning, evaluation, evidence synthesis, and AI systems that support hypothesis generation and decision-making in complex research environments.

\medskip

\noindent\textbf{Arindam Sett.}
\textit{Roche / Genentech;
\href{mailto:sett.arindam@gene.com}{sett.arindam@gene.com}.}
Principal Machine Learning Engineer at Genentech focused on AI data readiness, scientific AI platforms, retrieval-augmented systems, and agentic workflows. His work spans data foundations, knowledge systems, and AI infrastructure for scientific discovery, with a particular interest in understanding how data ecosystems influence downstream AI behavior.

\normalsize

\subsection{Why This Team Can Deliver the Workshop}
\label{sec:org-fit}
The team spans industry research labs and academia, with combined expertise across applied ML for biomedical and scientific data, foundation models for science, scientific data infrastructure, and trustworthy/data-centric AI. The team intentionally blends senior organizers with first-time workshop organizers (two members) to support junior involvement while maintaining organizational experience. Outreach is already underway, with anchor speakers confirmed across AI for Science, foundation models, scientific infrastructure, and biomedical AI. The organizing team has assembled an initial reviewer pool of 44 researchers spanning academia, biotech, scientific infrastructure, and industry research, providing immediate capacity for workshop review and community outreach. The workshop website, CFP, OpenReview venue, reviewer recruitment plan, and post-workshop artifact plan all have designated owners; OpenReview venue setup, CFP drafting, and reviewer recruitment have explicit owners on the team. The team is intentionally diverse across gender, institution type (industry research, academic, biotech), geography (US, Israel), and career stage.

\subsection{Diversity of the Organizing Team}
\label{sec:org-diversity}
The organizing team is diverse across gender, institution type, geography, seniority, and discipline. The team spans pharmaceutical research, academic research, scientific infrastructure, biotech platforms, and independent scientific-AI organizations, with members across the US, and Israel. The organizers intentionally bridge scientific ML, biomedical AI, data systems, provenance, foundation models for science, and production AI infrastructure. The CFP and PC recruitment will explicitly extend beyond the organizers' immediate professional networks through university mailing lists, professional societies, social media, and cross-institutional outreach to broaden representation across geography, career stage, institution type, and research perspective.

\subsection{Program Committee Plan and Roster}
\label{sec:pc}

We are assembling a Program Committee of 40--50 reviewers before the CFP launch. Assuming 40--50 submissions and three reviews per submission, this target keeps the expected reviewer load at or below three papers per reviewer. If submissions exceed 50, we will expand the PC or appoint area chairs to maintain review quality and timely decisions.

The PC is organized around expertise clusters aligned with the workshop's two tracks: AI-facing scientific data infrastructure; evaluations for scientific AI; workflow systems and deployed analysis tools; biomedical and scientific AI applications; industrial assay platforms; reproducibility, failure analysis, and human review. Each submission will be assigned to reviewers with matching technical expertise, and COI checks will be performed through OpenReview before assignments are finalized. The named roster below reflects the current confirmed reviewer pool.

\noindent\textbf{Current confirmed reviewer pool.}\par\vspace{2pt}

\noindent{\scriptsize
\setlength{\tabcolsep}{2pt}
\renewcommand{\arraystretch}{1.05}
\begin{tabular}{@{}p{0.49\textwidth}p{0.49\textwidth}@{}}
R01: J. Karin --- HUJI & R23: J. Liu --- Genentech \\

R02: K. Pang --- Stanford & R24: H. M. Khiem --- University of Cincinnati \\

R03: M. Schaefer --- Stanford & R25: M. Patel --- Walmart \\

R04: K. Ponsin --- Rockefeller & R26: O. Bazgir --- Oracle \\

R05: A. Ghandehari --- UC Irvine & R27: J. Rossen --- Harvard \\

R06: A. Gorla --- UCLA & R28: V. Shitov --- Helmholtz \\

R07: A. Shafran --- ETH Zurich & R29: N. Walter --- CISPA \\

R08: S. Nair --- Genentech & R30: A. Fomitchev --- UC Santa Cruz \\

R09: A. Gupta --- Stanford & R31: S. Joshi --- Intuit \\

R10: M. Bereket --- Stanford & R32: S. Kurant --- Technion \\

R11: A. Wu --- Genentech & R33: Y. Lee --- Xaira \\

R12: N. Mudrik --- Johns Hopkins & R34: Y. Shamay --- Technion \\

R13: R. Mintz --- HUJI & R35: R. Littman --- Genentech \\

R14: R. Friedman --- HUJI & R36: E. Peterfreund --- Yale \\

R15: W. Cheng --- Carnegie Mellon & R37: P. Gajare --- UC Irvine \\

R16: Z. Zhu --- UC Berkeley & R38: N. Azran --- HUJI \\

R17: R. Lacombe --- HCVC & R39: M. Danziger --- IBM \\

R18: P. Ogden --- Manifold Bio & R40: M. Osman --- Polyphron \\

R19: Z. Yang --- LatchBio & R41: L. Nuzhna --- Impetus Grants \\

R20: H. Bhasin --- TwentyTwo Bio & R42: J. Wang --- Harvard \\

R21: P. Pao-Huang --- Stanford & R43: S. Alber --- Stanford \\

R22: T. Kitak --- ETH Zürich & R44: E. De Brouwer --- Genentech \\

\end{tabular}
}

\vspace{2mm}
\textit{\noindent Additional reviewers will be recruited if needed.}

\subsection{Other Workshops the Organizers are Concurrently Proposing}
\label{sec:org-concurrent}
No listed organizer is concurrently proposing another NeurIPS 2026 workshop. 

% =====================================================================
% References (unlimited; outside the 3+2 page limit).
% =====================================================================
\clearpage
\setproposalpart{References}
\proposalbanner{References}{Outside the 3+2 page limit}
\renewcommand{\refname}{References}
\begin{thebibliography}{99}

\bibitem{wilkinson2016fair}
M. D. Wilkinson, M. Dumontier, I. J. Aalbersberg, G. Appleton, M. Axton, A. Baak, et al.
\newblock The FAIR Guiding Principles for scientific data management and stewardship.
\newblock \emph{Scientific Data}, 3:160018, 2016. \href{https://doi.org/10.1038/sdata.2016.18}{doi:10.1038/sdata.2016.18}.

\bibitem{Gonzalez-Espinozaaiready}
Alfredo Gonzalez-Espinoza
\newblock AI-ready Research Data
\newblock 2026. \href{https://guides.library.cmu.edu/ResearchDataForAI}{https://guides.library.cmu.edu/ResearchDataForAI}

\bibitem{gebru2021datasheets}
T. Gebru, J. Morgenstern, B. Vecchione, J. W. Vaughan, H. Wallach, H. Daum\'{e} III, and K. Crawford.
\newblock Datasheets for datasets.
\newblock \emph{Communications of the ACM}, 64(12):86--92, 2021. \href{https://doi.org/10.1145/3458723}{doi:10.1145/3458723}.

\bibitem{pushkarna2022datacards}
M. Pushkarna, A. Zaldivar, and O. Kjartansson.
\newblock Data Cards: Purposeful and Transparent Dataset Documentation for Responsible AI.
\newblock In \emph{ACM FAccT}, 2022. \href{https://doi.org/10.1145/3531146.3533231}{doi:10.1145/3531146.3533231}.

\bibitem{akhtar2024croissant}
M. Akhtar, O. Benjelloun, C. Conforti, L. Foschini, J. Giner-Miguelez, P. Gijsbers, S. Goswami, N. Jain, M. Karamousadakis, M. Kuchnik, et al.
\newblock Croissant: A Metadata Format for ML-Ready Datasets.
\newblock In \emph{NeurIPS Datasets and Benchmarks Track}, 2024.
\newblock \url{https://arxiv.org/abs/2403.19546}.

\bibitem{hiniduma2024survey}
K. Hiniduma, S. Byna, and J. L. Bez.
\newblock Data Readiness for AI: A 360-Degree Survey.
\newblock arXiv preprint arXiv:2404.05779, 2024.
\newblock \url{https://arxiv.org/abs/2404.05779}.

\bibitem{hiniduma2024aidrin}
K. Hiniduma, S. Byna, J. L. Bez, and R. Madduri.
\newblock AI Data Readiness Inspector (AIDRIN) for Quantitative Assessment of Data Readiness for AI.
\newblock In \emph{Proc. 36th Intl. Conf. on Scientific and Statistical Database Management (SSDBM)}, 2024. \href{https://doi.org/10.1145/3676288.3676296}{doi:10.1145/3676288.3676296}.

\bibitem{brewer2025scientific}
W. Brewer, P. Widener, V. Anantharaj, F. Wang, T. Beck, A. Shankar, and S. Oral.
\newblock Data Readiness for Scientific AI at Scale.
\newblock In \emph{Proc. 54th Intl. Conf. on Parallel Processing Companion (ICPP Companion)}, 2025.
\newblock \url{https://arxiv.org/abs/2507.23018}.

\bibitem{brewer2026pipeline}
W. Brewer, P. Widener, V. Anantharaj, F. Wang, T. Beck, A. Shankar, and S. Oral.
\newblock Data readiness pipeline patterns for scientific AI at scale: Insights from climate, fusion, life sciences, and materials.
\newblock \emph{AI Magazine}, 2026. \href{https://doi.org/10.1002/aaai.70056}{doi:10.1002/aaai.70056}.

\bibitem{majithia2026actionable}
N. Majithia, T. Carey-Wilson, E. Simperl, and N. Shadbolt.
\newblock An actionable framework for AI-ready data.
\newblock \emph{AI Magazine}, 2026. \href{https://doi.org/10.1002/aaai.70054}{doi:10.1002/aaai.70054}.

\bibitem{bhardwaj2024curation}
E. Bhardwaj, H. Gujral, S. Wu, C. Zogheib, T. Maharaj, and C. Becker.
\newblock The State of Data Curation at NeurIPS: An Assessment of Dataset Development Practices in the Datasets and Benchmarks Track.
\newblock In \emph{NeurIPS Datasets and Benchmarks Track}, 2024. \url{https://arxiv.org/abs/2410.22473}.

\bibitem{wu2024management}
Y. Wu, L. Ajmani, S. Longpre, and H. Li.
\newblock A Systematic Review of NeurIPS Dataset Management Practices.
\newblock In \emph{NeurIPS Datasets and Benchmarks Track}, 2024. \url{https://arxiv.org/abs/2411.00266}.

\bibitem{hbr2026taming}
Harvard Business Review Analytic Services.
\newblock \emph{Taming the Complexity of AI Data Readiness}.
\newblock HBR Analytic Services Pulse Survey, sponsored by Cloudera, 2026.
\newblock \url{https://hbr.org/resources/pdfs/comm/cloudera/TamingtheComplexityofAIDataReadiness.pdf}.

\bibitem{ai4science2025}
AI for Science Community.
\newblock The Reach and Limits of AI for Scientific Discovery: NeurIPS 2025 AI for Science Workshop.
\newblock \url{https://ai4sciencecommunity.github.io/neurips25}.

\bibitem{ml4ps2025}
Machine Learning and the Physical Sciences Workshop Organizers.
\newblock Machine Learning and the Physical Sciences, NeurIPS 2025.
\newblock \url{https://ml4physicalsciences.github.io/2025/}.

\bibitem{fm4ls2025}
FM4LS Workshop Organizers.
\newblock NeurIPS 2025 Workshop on Multi-modal Foundation Models and Large Language Models for Life Sciences.
\newblock \url{https://nips2025fm4ls.github.io/}.

\bibitem{dmlr2025}
Data-centric Machine Learning Research Community.
\newblock Data-centric Machine Learning Research Workshop.
\newblock \url{https://dmlr.ai/}.

\bibitem{reliableml2025}
Reliable ML Workshop Organizers.
\newblock Reliable ML from Unreliable Data: NeurIPS 2025 Workshop.
\newblock \url{https://reliablemlworkshop.github.io/}.

\bibitem{adsd2025}
ADSD Workshop Organizers.
\newblock The 1st Workshop on AI-Ready Data for Science Discovery at ICDM 2025.
\newblock \url{https://cnicds.github.io/ICDM2025/}.

\bibitem{afzal2020datareadiness}
S. Afzal, C. Rajmohan, M. Kesarwani, S. Mehta, and H. Patel.
\newblock Data Readiness Report.
\newblock In \emph{IEEE Intl. Conf. on Smart Data Services}, 2020. \url{https://arxiv.org/abs/2010.07213}.

\end{thebibliography}

\end{document}
